Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-05-29 supplement.tex
started deleting material already present in the paper.

\section{Introduction}
\citet{rappaport} first reported the discovery of a highly unusual stellar system in the Kepler field.
KIC 12557548's (hereafter \shStar's) light curve exhibited periodic flux dips with a period of 0.653 days.
What was highly unusual about \shStar\ was that the flux dips were neither symmetric in shape nor constant in amplitude, varying from $\sim$ 0\% to $\sim$ 1.2\%.
The variations in amplitude are highly stochastic and unpredictable from one event to the next 0.653 days later.
This indicates the creation and clearing of material that can cover up to 1\% of the star in $\lesssim$ 1 day timescales.
These variable dips are best explained as dust extinction from material that is escaping a rocky planet (KIC 12557548 b, hereafter \sha) in a short period orbit.
The \shStar\ system has the exciting possibility of being an opportunity to study a planet that has been peeled away layer by layer to reveal an interior core.

The discovery of K2-22b \citep{sanchis-ojedak2-22}, WD 1145+017 \citep{vanderburg2015wdDisintegrating}, KOI 2700 \citep{rappaport2014KOI2700} showed that other systems have similar light curves and that other disintegrating planet systems may be useful laboratories for understanding disintegrating planets.
Multi-wavelength light curve measurements show that the dust particles can have wavelength-dependent transmission, as predicted from sub-micron dust particles \citep{bochinski2015evolving,sanchis-ojedak2-22}.

Furthermore, there are perplexing systems that also display stochastic transit behavior but for which there are still no agreed-upon explanations: KIC 8462852 (ie. Boyajian's star) \citep{boyajian846}, RIK-210 \citep{david2017rik210} and PTFO 8-8695 \citep{vanEyken2012ptfTTauri}.
KIC 8462852 may be a family of comets from one or more parent bodies that recently were broken apart.
RIK-210 and PTFO 8-8695 are both in young systems ($\lesssim$ 10 and $\lesssim$3 Myr respectively) so they may be proto-planets.
RIK-210 may have accreting material that causes variable extinction.
PTFO 8-8695's orbit may be precessing and causing variations in transit depth depending on its longitude.

Observational evidence from the \shStar\ system puts constraints on the planet candidate on the system.
Radial velocity velocity variations of the host star put an upper limit on the reflex motion due to the planet and constrains the mass to be $\lesssim 1.2 M_{\mathrm Jup}$ \citep{croll2014}.
There is no detection of secondary eclipses of \sha\ with a 3$\sigma$ upper limit of $5 \times 10^{-5}$ in the Kepler bandpass, which means that for an albedo of 0.5, the radius of the planet must be smaller than 4600 km.
The timescale of the variability of the transits gives a mass lot rate of order $\sim M_\oplus/Gyr$, which would indicate a present-day mass of 0.014 $M_\oplus$ when using a radiative-hydrodynamic wind model \citep{perez-becker}.

The Kepler spacecraft performed near-continuous long cadence photometry for KIC 12557548 during its entire main mission lifetime from 2009 to 2013.
During this time, the transit depths averaged around $\sim$0.6\% but varied stochastically from just one 15.7 hour orbit to the next.
\citet{vanWerkhoven2014} analyzed 15 of the total 17 quarters of data and calculated every transit depth during this period.
There were two intervals near obits 50 and 1950 that showed shallower (0.1\%) than average transit depths for roughly one month.

Subsequently, \citet{schlawin2016kic1255} observed 8 total transits of the system for 4 nights in 2013 and 4 nights in 2014 for the $r'$ band using the MORIS imager \citep{Gulbis2011} on SpeX/IRTF \citep{rayner03}.
\citet{schlawin2016kic1255} found that the transit depths were all weaker than $0.43\%$ and that the probably of this randomly occurring based on random behavior from Kepler statistics was around 0.2\%.
This was evidence that the observations occured during weaker periods (as found in \citet{vanWerkhoven2014}'s 15 Kepler quarter analysis) or that the disintegration activity was falling off with time.
We performed follow-up $R$ band photometry of the \shStar\ system to explore whether the disintegration activity is shutting off with time.

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
We obtained photometry for 5 nights with good weather on the \sha\ system.

\subsection{Previous Observations}

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
\enddata
\tablenotetext{}{Summary of published photometric observations of \sha.}
\end{deluxetable*}

@@

For the photometric reduction, we used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/stamps_kic1255_UT2016_07_14.pdf}
\caption{Target (src) and reference stars (numbered) used on UT 2016-07-14.
The reference stars were chosen to have similar count levels as the source. 
}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}

>>>>

\section{Introduction}
Supplementary Material/Notes for the main paper

\section{Observations}

@@

For the photometric reduction, I used the \texttt{ccdproc} package to generate master flat field and bias files.
I combined with an average with a low threshold of 2$\sigma$ and a high threshold of 5$\sigma$.

As an initial start, I created a time series for the night of UT 2016-06-12.
I used aperture photometry with a source radius of 4 pixels, an inner aperture annulus of 5 pixels and an outer aperture radius of 8 pixels for the background.
I choose 6 reference stars of similar brightness and which were nearby the source on the CCD.
I use the \texttt{photutils} python package for the aperture photometry.
The resulting raw time series can be seen in \ref{fig:initTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{initial_t_series.pdf}
\caption{Quick raw time series for UT 2016-06-12. No aperture centering was done (there were fixed apertures with time).
No bias or flat field corrections were applied.}\label{fig:initTseries}
\end{centering}
\end{figure}

The initial time series has huge fluctuations (and even goes negative! due to poor aperture centering at the start).
I used \texttt{photutils.centroid\_2g} to do 2D Gaussian centroiding to choose the aperture positions to start with.
The guess position and \texttt{centroid\_2g} position for the target \sha\ are shown in Figure \ref{fig:centroid2g}.
Adding a centroiding routine significantly improves the precision as seen in Figure \ref{fig:secTseries}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{centering.pdf}
\caption{The guess position of (750.7,682.4) is shown as a cyan circle. The \texttt{centroid\_2g} position of (749.7,681.1) is shown as a red circle.}\label{fig:centroid2g}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time aperture centroiding was done.
No bias or flat field corrections were applied.}\label{fig:secTseries}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_bias_flat.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
This time bias correction, flat field correction and aperture centroiding was done.
Note that the target, reference stars 2 and 3 have smaller deviations at 0.81 days.}\label{fig:secTseriesBiasFlat}
\end{centering}
\end{figure}

It turns out that the large flux excursions in Figure \ref{fig:secTseries} and \ref{fig:secTseriesBiasFlat} are due to some bumps pointing errors and so substantial fractions of flux fall outside the source apertures.
I solved this problem by increasing the size of the subarray box (from 10 pix width to 18 px) so that the source would be found even if it wanders.
This results in much smaller flux excursions, as seen in Figure \ref{fig:secTseriesWiderBox}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{second_t_series_wider_box.pdf}
\caption{Same data for UT 2016-06-12 as Figure \ref{fig:initTseries}.
Bias correction, flat field correction and aperture centroiding was done.
The aperture centering (2D Gaussian fits) was performed with a wider 18 pixel box to allow for pointing wander.}\label{fig:secTseriesWiderBox}
\end{centering}
\end{figure}

We considered several ways to do reference summation.
Under consideration were two choices:
\begin{itemize}
	\item How to weight the stars (by flux, equally, variance)?
	\item Which stars to include in the summation?
\end{itemize}
Figure \ref{fig:refSumMethods} shows these 4 combinations of these two choices.
Clearly reference star 2 adds noise to the time series, but this does not affect the total summation method since it has lower flux.
When normalizing each time series before summation, this appears to decrease the linear trend in the data.
In all cases, there is an apparent transit-like feature near JD = 2457551.82.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/reference_method.pdf}
\caption{Corrected time series for \shStar\ when using different combinations of averaging the reference stars: i) Summing all stars equally ii) Summing the best stars [1,3,4,5,6], iii) Summing the normalized time series of the best stars iv) summing the normalized time series of the best stars.}\label{fig:refSumMethods}
\end{centering}
\end{figure}

Figure \ref{fig:starLabels} shows the reference stars used in the initial analysis.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/st_labels.pdf}
\caption{\shStar\ at the center and the reference stars used for the photometry.}\label{fig:starLabels}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps.pdf}
\caption{Postage stamps of apertures used for each source (before centroiding).}\label{fig:starPostageGuess}
\end{centering}
\end{figure}

Source centroiding was performed with \texttt{centroid\_2g} within \texttt{photutils} to do 2-D Gaussian fitting. Figure \ref{fig:starPostageCen}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_centered.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding with \texttt{centroid\_2g} with the initial guesses shown in Figure \ref{fig:starPostageGuess}.}\label{fig:starPostageCen}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/postage_stamps_r09px_cen.pdf}
\caption{Postage stamps of apertures used for each source, after centroiding and using a wider 9 pixel source aperture.}\label{fig:starPostageCenAp9px}
\end{centering}
\end{figure}

When using a wider aperture (9 pixels), the photometric stability is much improved and the 0.5\% transit depth is readily visible in Figure \ref{fig:refCorrectedPhotJun12}.
The Kepler-based ephemeris indicates a transit at JD = 2457551.830.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_01.pdf}
\caption{Reference-corrected photometry for \shStar\ near the transit at JD = 2457551.830 (UT 2016-06-12).}\label{fig:refCorrectedPhotJun12}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/refcor_aug14.pdf}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14.}\label{fig:refCorrectedPhotJun14}
\end{centering}
\end{figure}

I experimented with a whole new set of reference stars (shown in Figure \ref{fig:newRefStars}) to see if they would work better for the time series on UT 2016-06-14.
I ended up with a very similar time series, as see in Figure \ref{fig:refCorrectedPhotJun14newStars}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/st_labels}
\caption{A new set of reference stars that matched the source better in terms of brightness.}\label{fig:newRefStars}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_04_14_analysis/refcor_01}
\caption{Reference-corrected photometry for \shStar\ on UT 2016-06-14, using a new set of reference stars shown in Figure \ref{fig:newRefStars}.}\label{fig:refCorrectedPhotJun14newStars}
\end{centering}
\end{figure}

The time series from UT2016-07-14 showed a sharp drop in flux for all stars as seen in Figure \ref{fig:ut2016-07-14clouds}.
Turns out is clouds, as visible in Figure \ref{fig:ut2016-07-14cloudImg}.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/ut2016_07_14_tser_allstars.pdf}
\caption{All stars' photometry for \shStar\ on UT 2016-07-14.
There is a sharp drop in flux at 32.88 due to clouds}\label{fig:ut2016-07-14clouds}
\end{centering}
\end{figure}

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_152.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_162.pdf}
\includegraphics[width=0.5\textwidth]{images/ut2016_07_14_clouds/figure_index_166.pdf}
\caption{Three example images during a cloud passage.}\label{fig:ut2016-07-14cloudImg}
\end{centering}
\end{figure}
